JD notes on effects

### 2022-07-27 manuscript/body.tex
hand over

In \FREF{pred_bin_prediction_effects_plots}, we use the results in \FREF{pred_bin_plots}A and compare the prediction and effect plots associated with the central estimates. 
%
\begin{figure}
\begin{center}
\includegraphics{glm_two_predictor_preds_effects.ggp.pdf}
\end{center}
\caption{{\bf Bias correction for prediction and effect plots.} 
As in \FREF{pred_bin_plots}, the observed-value based estimates match the pattern of the data better than mean-based estimates. 
\jd{Fix the caption (maybe we should say “central, effects, predictions”). I don't think you need to repeat again about central estimates being the same.}
\jd{Add “data mean” as a horizontal line to the plots? I think data mean might be a good name, actually.
}
\label{fig:pred_bin_prediction_effects_plots}
\end{figure}

@@

\jd{We should maybe discuss mediated effects and other stuff. We need to be much clearer about chains of causality and this example. Let's not say “somehow”}
A \emph{mediated} effect is a situation in which only some of the input variables have a \emph{causal} impact on the outcome, even though all the variables are (somehow) associated with the outcome. For example, psychological factors such as water taste in the relationship between household socio-economic status and improved water quality status.

@@

The mean-based approach is widely used to create outcome plots. However, in a model with complex interaction, MPVs or categorical variables, it is sensitive to the choice of the reference point. We have demonstrated that a non-focal model-center-based reference point is generally a stable choice and provides estimates more consistent with the observed quantities as compared to common input-variable mean-based approach.

@@

Our simulation examples focused on simple linear and logistic models due to their wide range of usage and application. These models also act as a starting point for building other complex models, including mixed effect models and models with categorical predictors. The logic for extending to more complex models, including other forms of non-linear link functions, is very straightforward. The components needed for extension are the correct linear predictor and the inverse link function; everything else generalizes. In addition, our \proglang{R} package implementation already extends to and supports most of the non-linear link functions and mixed model framework, including multivariate binary outcome models.

>>>>

In \FREF{pred_bin_prediction_effects_plots}, we use the results in \FREF{pred_bin_plots}A and compare the prediction and effect plots associated with the central estimates. 
%
\begin{figure}
\begin{center}
\includegraphics{glm_two_predictor_preds_effects.ggp.pdf}
\end{center}
\caption{{\bf Bias correction for prediction and effect plots.} 
As in \FREF{pred_bin_plots}, the observed-value based estimates match the pattern of the data better than mean-based estimates. 
\jd{Fix the caption (maybe we should say “central, effects, predictions”). I don't think you need to repeat again about central estimates being the same.}
\jd{Add “data mean” as a horizontal line to the plots? I think data mean might be a good name, actually.}
}
\label{fig:pred_bin_prediction_effects_plots}
\end{figure}

@@

\jd{We should maybe discuss mediated effects and other stuff. We need to be much clearer about chains of causality and this example. Let's not say “somehow”}
A \emph{mediated} effect is a situation in which only some of the input variables have a \emph{causal} impact on the outcome, even though all the variables are (somehow) associated with the outcome. For example, psychological factors such as water taste in the relationship between household socio-economic status and improved water quality status.
\jd{Maybe a good example for this would be using education as a mediator for effects of wealth? Can you think of a better one?}

@@

The mean-based approach is widely used to create outcome plots. However, in a model with complex interaction, MPVs or categorical variables, it is sensitive to the choice of the reference point. We have demonstrated that a non-focal model-center-based reference point is generally a stable choice and provides estimates more consistent with the observed quantities as compared to common input-variable mean-based approach.
\jd{I don't feel we need to say “non-focal” -- “-based” really covers it.}

@@

Our simulation examples focused on simple linear and logistic models due to their wide range of usage and application. These models also act as a starting point for building other complex models, including mixed effect models and models with categorical predictors. The logic for extending to more complex models, including other forms of non-linear link functions, is straightforward. The components needed for extension are the correct linear predictor and the inverse link function; everything else generalizes. In addition, our \proglang{R} package implementation already extends to and supports most of the non-linear link functions and mixed model framework, including multivariate binary outcome models.
